\documentclass[10pt]{report}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

\setlist[itemize]{leftmargin=0ex}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\begin{document}

\textbf{{\Huge Andrew January}}

Flat 2, 4 Lorne Street, Reading, Berkshire, RG1 7YN

\begin {tabular}{ll}
Email&andrewjanuary@gmail.com \\
Tel&+44 7999 408105 \\
Skype&aJanuary
\end{tabular}

\section*{Objective}
I have several years experience working in a professional software development environment. During that time I have been pivotal in improving the automated tests, as well as automating some of the more error prone and laborious tasks in the development lifecycle.

I am now looking to work at a company with a culture that values modern software development practices, such as test-driven development, so that I can focus on growing my skills as a developer and learning new technology alongside smart and motivated people.

I would also like to work on a new technology stack such as one built on Ruby.

\section*{Technical Skills}
\setdescription{style=multiline,topsep=10pt,leftmargin=4.5cm,font=\normalfont}
\begin{description}
  \item[Programming Languages]
    C\# (7 years), Java (4 years), Ruby, Javascript, SQL, Python, \mbox{Objective-C}, PHP, Delphi, Flex, TCL
  \item[Technologies and Libraries]
    jQuery, JSON, HTML, XML, Sinatra, Apache Server, Tomcat, Ivy, Spring, jUnit, Mockito
  \item[Operating Systems]
    Windows (7 years), OS X (6 years), Linux (Slackware and Ubuntu, 6 years)
  \item[IDEs and Editors]
    Vim, Eclipse, Visual Studio
  \item[Source Control]
    Git, Subversion, CVS
\end{description}

\section*{Experience}
\setdescription{style=multiline,topsep=10pt,leftmargin=3cm,font=\normalfont}
\begin{description}
  \item[2012 -- Present]
    \textbf{Evertz Microsystems Ltd.} \\
    Software Developer

    Evertz provides hardware and software to broadcasting companies worldwide to manage video media as well as scheduling and executing video playout.

    In my current role I develop and maintain a Java based product called Mediator: an Apache Tomcat hosted application that exposes a Flex UI used by broadcast operators. It uses a service oriented architecture as well as an XY redundancy model to provide high availability.

    I have been instrumental in several features and innovations:

    \begin{itemize}
      \item Wrote the implementation of the US government Emergency Alert System for the Public Broadcasting Service. A Java daemon receives national alerts and transforms them into a schedule of video events to show weather warnings and live Presidential broadcasts.
      \item Helped develop a hub-and-spoke model of redundancy, designing and implementing an XML based synchronisation protocol with timeouts and robustness against connectivity issues.
      \item Rewrote the Java and Delphi implementations of the in-house timecode mathematics library to increase precision and accuracy. I made careful consideration of backwards compatibility issues as it subtly changed the result of many previously incorrect calculations. I also refactored the test suite, drastically increasing coverage and removing many redundant tests.
      \item Introduced the dependency management tool Ivy into the development workflow, removing the need to manually manage dependencies and artifacts. I also created training material on Ivy for other developers.
      \item Implemented several extensions to the HTML/Javascript based configuration tool, including live previews of user-defined forms and the ability to resize and filter tables. This was done with a mix of Javascript, jQuery and modifications to the in-house annotation driven Java bean serializer/deserializer.
      \item Added automated unit testing to the configuration tool using Jasmine and PhantomJS, as well as a wrapper to allow it to be driven from the ant build tool and Eclipse.
    \end{itemize}

  \pagebreak[2]
  \item[2010 -- 2012]
    \textbf{OpenBet Technologies Ltd.} \\
    Software Developer

    OpenBet supplies online casino games to operators worldwide.

    I developed the Java server-side logic for games, running on top of an Apache Tomcat Servlet that exposed an XML API to be consumed by third part front-ends.

    I regularly worked through a large part of the software lifecycle, from design to implementation to support.

    \begin{itemize}
      \item Successfully developed a large number of games that were deployed on several customer's websites.
      \item Implemented two new game engines being used as the basis for games written by myself and other developers.
      \item Introduced the use of automated testing tools such as Cucumber's executable specifications to improve regression testing, reduce bugs and help ensure the specifications were met correctly.
      \item Wrote technical design documentation for dozens of games that were subsequently turned into successful implementations by myself and other developers.
      \item Led a team of five people in the analysis and merging of two previously separate TCL web front-end codebases into a single, more maintainable product.
      \item Mentored new colleagues and provided pivotal support to the technical lead during the formation of a new team.
      \item Provided on-site developer support for a major customer website upgrade.
      \item Worked directly with customers in the statistical analysis and subsequent debugging of games to ensure they met their specifications.
    \end{itemize}

  \pagebreak[2]
  \item[2010 -- 2011]
    \textbf{DiaCon (Harry Potter Conference)}
    \begin{itemize}
      \item Programmed the conference website using PHP, HTML and Javascript, including the registration and payment pages.
      \item Wrote a responsive web-app for the conference schedule that allowed people to view and favourite programme items. I made use of HTML5's local storage APIs and manifest files to make it work seamlessly both offline and online.
      \item Helped with the successful planning and running of the event.
    \end{itemize}

  \pagebreak[2]
  \item[2010]
    \textbf{Mew (Open Source Programming Language)} \\
    http://code.google.com/p/mew-lang
    \begin{itemize}
      \item Designed and implemented new language features, test suites and formal specification.
    \end{itemize}

  \pagebreak[2]
  \item[2009 -- 2010]
    \textbf{Chair of Departmental Student Society, University of York}
    \begin{itemize}
      \item Organised and chaired weekly committee meetings.
      \item Chaired the organisation and running of events.
      \item Worked to reform the society structure, and therefore achieve ratification from the University of York Students' Union.
    \end{itemize}
\end{description}

\section*{Education}
\begin{description}
  \item[2007--2010]
    \textbf{BEng Hons Computer Science, University of York} \\
    2:1. Dissertation on \textit{Adding Entry-Exit Coverage to Haskell Program Coverage}.

  \item [2004 -- 2007]
    \textbf{Orpington College, Bromley, Kent} \\
    A Levels: Computing~---~A, Psychology~---~A, Mathematics~---~B, English Literature~---~C
\end{description}

\section*{Personal}
I play board games and regularly attend a friend's board games night with my wife. I enjoy going to live stand-up gigs and listen to a number of comedy podcasts.

\end{document}